Fourmile

### 2022-09-07 fourmile_dataprocess.Rmd
next steps: clean up precip eval, get prism daily srad data

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
library(kableExtra)
library(dataRetrieval)
library(raster)
library(sf)
library(stringr)

@@

## Compare Niwot SNOTEL pirecip to prism pixel

@@

@@

niwot_prismshift <- niwot_compare %>%
  mutate_at(c("prism_mm"), funs(lead), n = 1) %>%
  mutate(month = month(date)) %>%
  filter(!month %in% c(6:8)) %>%
  mutate(diff_mm = snotel_mm - prism_mm)

summary(niwot_prismshift)

@@

>>>>

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
library(kableExtra)
library(dataRetrieval)
library(raster)
library(sf)
library(stringr)
library(hydroGOF)
library(Metrics)
```

@@

## Compare Niwot SNOTEL precip to prism pixel

@@

rmse(niwot_compare$prism_mm, niwot_compare$snotel_mm)
pbias(niwot_compare$prism_mm, niwot_compare$snotel_mm)

scatter <- ggplot(niwot_compare, aes(x=snotel_mm, y=prism_mm)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue")

ggplotly(scatter)

@@

niwot_prismshift <- niwot_compare %>%
  mutate_at(c("prism_mm"), funs(lead), n = 1) %>%
  mutate(month = month(date)) %>%
  #filter(!month %in% c(6:8)) %>%
  mutate(diff_mm = snotel_mm - prism_mm)

summary(niwot_prismshift)
rmse(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
NSE(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
pbias(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)

scatter_shiftday <- ggplot(niwot_prismshift, aes(x=snotel_mm, y=prism_mm)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue")

ggplotly(scatter_shiftday)

niwot_prismfrac <- niwot_compare %>%
  mutate(prism_most_mm = prism_mm * 0.974,
         prism_little_mm = prism_mm * 0.026) %>%
  mutate_at(c('prism_most_mm'), list(lead), n = 1) %>%
  mutate(prism_new_mm = prism_most_mm + prism_little_mm,
         diff_prismfrac = snotel_mm - prism_new_mm)

summary(niwot_prismfrac)

scatter_frac <- ggplot(niwot_prismfrac, aes(x=snotel_mm, y=prism_new_mm)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue")

ggplotly(scatter_frac)

rmse(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
NSE(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
pbias(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)

@@

## Compare prism solar rad to flux solar rad

```{r}
srad <- solr %>%
  dplyr::select(-1) %>%
  filter(!row_number() %in% c(1:17)) %>%
  replace(.==-9999, NA) %>%
  rename(date = 1,
         prism_w = 2,
         prism_m = 3,
         prism_e = 4,
         gordon_s = 5,
         gordon_n = 6,
         greenlake = 7) %>%
  mutate(date = dmy(date))

niwot_srad <- Niwo %>%
  mutate(date = ymd(date))

niwot_daymet <- daym %>%
  filter(!row_number() %in% c(1:7)) %>%
  rename(year = 1,
         doy = 2,
         srad_wm2 = 3)
